Hydras \& Co.

### 2022-03-19 doc/part-hydras.tex
corrections chapter 7 (completed)

Since we won't be able to prove the proposition
\linebreak \Verb|{exists! a: Ord, least_member (Empty_set Ord) a|, the only properties we would be able to prove about \texttt{bottom} would be \emph{trivial} properties, 
\emph{i.e.}, satisfied by \emph{any} element of type \texttt{Ord}, like for instance
\texttt{bottom = bottom}, or \texttt{zero <= bottom}.

@@

>>>>

Since we won't be able to prove the proposition
\linebreak \Verb|(exists! a: Ord, least_member (Empty_set Ord) a)|, the only properties we would be able to prove about \texttt{bottom} would be \emph{trivial} properties, 
\emph{i.e.}, satisfied by \emph{any} element of type \texttt{Ord}, like for instance
\texttt{bottom = bottom}, or \texttt{zero <= bottom}.

@@

\begin{todo}
  Build a T2Bridge! (note: Gamma0's wellfoundedness is missing in \gaia (?).
\end{todo}
